---
title: "Week 02 Exercise"
output: html_document
---

[ ] - indexing positions

```{r}
m <- 1:100
m

m[1:15]
```
Matthew on single and double brackets: I think things might start to make a bit more sense when we get to indexing list indices e.g., list[[2]][1,2] vs list[2][1,2] (second one will return an error)

Tony's example of creating your own Data Frame: Love the Walking Dead reference

```{r}
df <- df <-
  data.frame(
    firstName = c("Rick", "Negan", "Dwight", "Maggie", "Michonne"),
    community = c("Alexandria", "Saviors", "Saviors", "Hilltop", "Alexandria"),
    sex = c("M", "M", "M", "F", "F"),
    age = c(42, 40, 33, 28, 31)
  )
df # will display data frame
```

When reading csv file Remember to copy PATH exactly as it is presented and remember to use commas (,) between each field in read.csv

```{r}
df <- read.csv(file = "~/Documents/Documents/class_folders/ada/repos/week-02-exercise/CPDS-1960-2014-reduced.csv", sep = "," , header = TRUE, stringsAsFactors = FALSE)
```

If you get a Error: unexpected symbol, make sure to check you have commas between each field. 
